Leaf traits drive differences in biomass partitioning among major plant functional types

### 2014-12-11 manuscript.Rnw
New panel in SI4, some caption updates

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure1.pdf}
    \caption{(a) Global coverage of the climate space by the dataset. Hexagons are terrestrial observations, excluding areas without woody vegetation, colored by number of 0.5\degree~cells, cut off at 6000mm MAP. Triangles are averages for the three PFTs across all contributed studies. (b) Schematic of a woody plant, and the variables considered in this study. H = plant height, $A_S$ basal stem area, $A_sbh$ stem area at 'breast height', $M_W$ woody biomass, $M_F$ leaf biomass (total aboveground biomass $M_T = M_F + M_W$), $A_F$ total leaf area.}
    \label{fig:figure1}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS1b.pdf}
    \caption{Mean annual precipitation (MAP) and temperature (MAT) for all contributed datasets, by vegetation type. MAP and MAT were taken from Worldclim \cite{worldclim}, using latitude and longitude reported for each contributed dataset.}
    \label{fig:figureS1}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure1.pdf}
    \caption{(a) Global coverage of the climate space by the dataset. Hexagons are terrestrial observations, excluding areas without woody vegetation, colored by number of 0.5\degree~cells. (b) Schematic of a woody plant, and the variables considered in this study. H = plant height, $A_S$ basal stem area, $A_{sbh}$ stem area at 'breast height', $M_W$ woody biomass, $M_F$ leaf biomass (total aboveground biomass $M_T = M_F + M_W$), $A_F$ total leaf area.}
    \label{fig:figure1}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureS1.pdf}
    \caption{Global coverage of the climate space by the dataset. Methods are as in Fig 1 in main text, symbols are colored by vegetation type as reported by the data contributors.}
    \label{fig:figureS1}
\end{figure}
